Equations & R Code

### 2016-09-07 manuscript/coexistence-stability_ms.Rmd
minor changes to intro paragraphs

INTRODUCTION
------------
@MacArthur1955, @Elton1958, and even Darwin [@Turnbull2013] recognized that species can compensate for each other and stabilize functioning in ecosystems subject to temporal variation in environmental conditions. 
This idea underlies the "insurance hypothesis" [@Yachi1999], which suggests stability increases with diversity because species respond dissimilarly to environmental conditions – species A has highest growth rates under conditions X whereas species B has highest growth rates under conditions Y. 
More species confer temporal stability by broadening the range of conditions under which the community maintains function [@Loreau2010].
Diverse models all predict a positive relationship between species richness and ecosystem stability [@Lehman2000; @Ives2002b; @Loreau2013], and experimental tests tend to support such a prediction [@Tilman2006; @Hector2010].
However, empirical support for a positive diversity-stability relationship is not unequivocal [@Jiang2009], and theory on the relationship between biodiversity and ecosystem stability often ignores the processes that determine species coexistence in variable environments [@Loreau2010].

For the benefits of biodiversity to be realized in the long term, species coexistence, which maintains biodiversity, must be stable [@Turnbull2013].
Contemporary coexistence theory can be divided into two broad classes: fluctuation-dependent mechanisms and fluctuation-independent mechanisms [@Chesson2000].
Classic work on resource partitioning [@Tilman1982] describes fluctuation-independent species coexistence, where stable coexistence depends on limiting resource requirements, not fluctuations in population abundances or environmental conditions.
In contrast, fluctuation-dependent coexistence mechanisms require the environment to fluctuate over time for species to coexist.
Indeed, the two most well-known fluctuation-dependent coexistence mechanisms, the storage effect and relative nonlinearity, depend on species-specific responses to environmental conditions, among other things, for species to stably coexist [@Chesson2004].
Thus, two forces can strengthen species coexistence: the uniqueness of their environmental responses and the variability of environmental conditions.
In other words, there is reason to expect environmental variability to promote species richness when coexistence is maintained by a fluctuation-dependent mechanism [@Adler2008].
Of course, increasing environmental variability may also decrease ecosystem stability through time by increasing the fluctuations of individual species, regardless of species richness.

@@

RESULTS
-------

@@

DISCUSSION
----------
The direction of the diversity-variability relationship can be positive and negative when species coexistence is maintained by fluctuation-dependent mechanisms (Fig. 2).
Ecosystem variability is positively correlated with species richness when species richness is measured across a gradient of envrionmental variability, which maintains diversity and promotes ecosystem variability (Fig. 2a,b).
If environmental conditions are sufficient to maintain coexistence, removing species increases ecosystem variability (Fig. 2c,d).
Thus, our results both confirm and contrast with theoretical and experimental findings that diversity begets stability.

@@

>>>>

INTRODUCTION
------------
@MacArthur1955, @Elton1958, and even Darwin [@Turnbull2013] recognized that species can compensate for each other and stabilize functioning in ecosystems subject to temporal variation in environmental conditions. 
This idea underlies the "insurance hypothesis" [@Yachi1999], which suggests stability increases with diversity because species respond dissimilarly to environmental conditions – species A has highest growth rates under conditions X whereas species B has highest growth rates under conditions Y. 
More species confer temporal stability by broadening the range of conditions under which the community maintains function [@Loreau2010].
Diverse models all predict a positive relationship between species richness and ecosystem stability [@Lehman2000; @Ives2002b; @Loreau2013], and experimental tests tend to support such a prediction [@Tilman2006; @Hector2010].
However, empirical support for a positive diversity-stability relationship is not unequivocal [@Jiang2009].
Furthermore, theory on the relationship between biodiversity and ecosystem stability often ignores the processes that determine species coexistence in variable environments [Loreau 2010, but see @Chesson2001].

Theoretical [@Chesson2000; @Chesson2004] and empirical [@Caceres1997; @Descamps-Julien2005; @Adler2006; @Angert2009] work has identified temporally fluctuating environmental conditions as an important ingredient for stable species coexistence.
Such "fluctuation-dependent" coexistence [@Chesson2000] requires that species have unique environmental responses and that environmental conditions vary enough for each coexisting species to experience good and bad conditions.
Thus, there is reason to expect environmental variability to promote species richness when coexistence is maintained by a fluctuation-dependent mechanism [@Adler2008].
Of course, increasing environmental variability may also decrease ecosystem stability through time by increasing the fluctuations of individual species, regardless of species richness.

<!--
For the benefits of biodiversity to be realized in the long term, species coexistence, which maintains biodiversity, must be stable [@Turnbull2013].
Contemporary coexistence theory can be divided into two broad classes: fluctuation-dependent mechanisms and fluctuation-independent mechanisms [@Chesson2000].
In contrast, fluctuation-dependent coexistence mechanisms require the environment to fluctuate over time for species to coexist.
Indeed, the two most well-known fluctuation-dependent coexistence mechanisms, the storage effect and relative nonlinearity, depend on species-specific responses to environmental conditions, among other things, for species to stably coexist [@Chesson2004].
Thus, two forces can strengthen species coexistence: the uniqueness of their environmental responses and the variability of environmental conditions.
In other words, 
-->

@@

RESULTS AND DISCUSSION
----------------------

@@

### The diversity-stability relationship
The direction of the diversity-variability relationship can be positive and negative when species coexistence is maintained by fluctuation-dependent mechanisms (Fig. 2).
Ecosystem variability is positively correlated with species richness when species richness is measured across a gradient of envrionmental variability, which maintains diversity and promotes ecosystem variability (Fig. 2a,b).
If environmental conditions are sufficient to maintain coexistence, removing species increases ecosystem variability (Fig. 2c,d).
Thus, our results both confirm and contrast with theoretical and experimental findings that diversity begets stability.

@@

### The impact of increasing environmental variability on ecosystem stability
